Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Mechanical Perturbations

### 2024-05-23 main.tex
Added placeholders for figures that Marten and I discussed.

@@

@@

\subsection{Protocol}
%
The subjects were divided into two groups, where the first group performed the
protocol at a belt speed of 10~\si{\kph} with the controller gain as $k=8$ and
the second group performed the protocol at a belt speed of 6~\si{\kph}. The
10~\si{\kph} group's experiments occured X weeks before the
6~\si{\kilo\meter\per\hour} group.

@@

>>>>

\todo[inline]{We should cite Leila's first paper and also the Pforzhiem work
(if there is something to cite).}

@@

\begin{figure}
  \includegraphics{example-image-a}
  \caption{Force nd torque plts of a pterubation of 80N per rope in the
  counterclockwise direction (from Marten's thesis, pg 26)}
\end{figure}

\begin{figure}
  \includegraphics{example-image-a}
  \caption{Thesis Fig 3.13 on pg 27}
\end{figure}

\begin{figure}
  \includegraphics{example-image-a}
  \caption{Thesis Fig 5.1 on pg 37}
\end{figure}

@@

\subsection{Protocol}
%
The subjects were divided into two groups. Tthe first group performed the
protocol at a belt speed of 10~\si{\kph} with the controller gain as $k=8$ and
the second group performed the protocol at a belt speed of 6~\si{\kph}. The
10~\si{\kph} group's experiments occured X weeks before the
6~\si{\kilo\meter\per\hour} group.

@@

\begin{figure}
  \includegraphics{example-image-a}
  \caption{Box plot or distrubtion plot showing graphical view of stats
  tables.}
\end{figure}
